Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
Adding a radius to plot for se or dispersion

df %>% 
  ggplot(., aes(x = xloc, y=yloc, 
                #group = run,
                color = indiv)) +
  facet_wrap(~run) +
  geom_path() +
  scale_color_manual(values = mycols) +
  geom_point(data = df %>% drop_na(s.id), 
             aes(x = xloc, y = yloc)) +
  geom_point(data = summ.df, aes(x = x, y=y), color = "black") +
  theme_bw()
```

>>>>

df %>% 
  ggplot(., aes(x = xloc, y=yloc, 
                #group = run,
                color = indiv)) +
  facet_wrap(~run) +
  geom_path() +
  scale_color_manual(values = mycols) +
  geom_point(data = df %>% drop_na(s.id), 
             aes(x = xloc, y = yloc)) +
  geom_point(data = summ.df, aes(x = x, y=y, size = dsprsn), color = "black") +
  theme_bw()
```
